### 2024-11-20 project2/nnMetamodels.tex
new

The single-stage procedure has three major advantages over the two-stage procedure:
\begin{enumerate}
    \item The single-stage procedure is expected to be more efficient than the two-stage procedure because it does not require the running the standard procedure in stage 2.
    \item The safety margin $\epsilon$ is not needed in the single-stage procedure.
    The safety margin is difficult to determine because it depends on the metamodel's accuracy in identifying true tail scenarios.
    The single-stage procedure does not need a safety margin because it directly estimates the risk measure using the predicted losses.
    \item Most importantly, the single-stage procedure is not limited to just estimating tail risk measures and can be extended to provide a broader assessment of risk. 
    It can be naturally adapted to estimate risk measures that require the knowing of the entire loss distribution, such as the standard deviation or the squared tracking error.
    Even for CVaR, the two-stage procedure become less attactive for an increased level.
    In our numerical experiments, we will compare the single-stage procedure to the two-stage procedure and the standard procedure in estimating the $\alpha$-CVaR for a lower $\alpha$.
\end{enumerate}

@@

\begin{table}[ht!]
    \small
    \centering
    \begin{tabular}{lccccc}
        \toprule
        \textbf{Model}      & \textbf{$N$}   & \textbf{Training error}   & \textbf{Test error}   & \textbf{True error}\\
        \midrule
        LSTM                & $100$                & $0.075 (\pm4.5\times 10^{-3})$        & $0.079(\pm5.4\times 10^{-3})$     & $0.063 (\pm4.4\times 10^{-3})$ \\ 
        High-capacity LSTM  & $100$                & $0.068 (\pm3.6\times 10^{-3})$        & $0.102(\pm6.1\times 10^{-2})$     & $0.060 (\pm3.6\times 10^{-3})$ \\
        Difference          & $100$                & $-0.007$                  & $0.023$               & $-0.003$ \\
        \hline
        LSTM                & $10$                 & $0.195 (\pm1.1\times 10^{-3})$        & $0.193(\pm1.7\times 10^{-3})$     & $0.070 (\pm9.1\times 10^{-4})$ \\
        High-capacity LSTM  & $10$                 & $0.157 (\pm2.0\times 10^{-3})$        & $0.199(\pm1.9\times 10^{-3})$     & $0.065 (\pm1.9\times 10^{-3})$ \\
        Difference          & $10$                 & $-0.038$                  & $0.006$               & $-0.005$ \\
        \hline
        LSTM                & $1$                  & $1.366 (\pm8.6\times 10^{-3})$        & $0.781(\pm6.0\times 10^{-3})$     & $0.129 (\pm5.0\times 10^{-3})$ \\
        High-capacity LSTM  & $1$                  & $1.354 (\pm2.7\times 10^{-2})$        & $0.795(\pm8.3\times10^{-2})$     & $0.149 (\pm2.7\times 10^{-2})$ \\
        Difference          & $1$                  & $-0.012$                  & $0.014$               & \textcolor{red}{$0.020$} \\
        \bottomrule
    \end{tabular}
    \caption{MSEs of LSTM metamodels.}
    \label{tab:lstm_arch}
\end{table}

@@

The accuracy and robustness of the LSTM metamodels motivate us to propose a single-stage procedure that uses the metamodel predictions to estimate the CVaR directly. 
Instead of relying on the standard nested simulation procedure in stage 2, the single-stage procedure is more efficient and extends to estimating other risk measures that require knowledge of the entire loss distribution.
In this section, we compare the single-stage procedure to the two-stage procedure and the standard procedure in estimating the $95\%$-CVaR of the hedging losses for GMWB.
In our numerical experiments, the results for the single-stage procedure is obtained with the same metamodels as in the two-stage procedure.
The only difference from Section~\ref{subsec:twoStageProcedure} is that the metamodel predictions are used to estimate the risk measures directly.

>>>>

The single-stage procedure has three major advantages over the two-stage procedure:
\begin{enumerate}
    \item The single-stage procedure is expected to be more efficient than the two-stage procedure because it does not require the running the standard procedure in stage 2.
    \item The safety margin $\epsilon$ is not needed in the single-stage procedure.
    The safety margin is difficult to determine because it depends on the metamodel's accuracy in identifying true tail scenarios.
    The single-stage procedure does not need a safety margin because it directly estimates the risk measure using the predicted losses.
    \item Most importantly, the single-stage procedure is not limited to just estimating tail risk measures and can be extended to provide a broader assessment of risk. 
    It can be naturally adapted to estimate risk measures that require the knowing of the entire loss distribution, such as the standard deviation or the squared tracking error.
    Even for CVaR, the two-stage procedure become less attactive for an increased level.
\end{enumerate}

@@

\begin{table}[ht!]
    \small
    \centering
    \begin{tabular}{lccccc}
        \toprule
        \textbf{Model}      & \textbf{$N$}         & \textbf{Training error}                & \textbf{Test error}               & \textbf{True error}\\
        \midrule
        LSTM                & $100$                & $0.075 (\pm4.5\times 10^{-3})$         & $0.079(\pm5.4\times 10^{-3})$     & $0.063 (\pm4.4\times 10^{-3})$ \\ 
        High-capacity LSTM  & $100$                & $0.068 (\pm3.6\times 10^{-3})$         & $0.102(\pm6.1\times 10^{-2})$     & $0.060 (\pm3.6\times 10^{-3})$ \\
        Average Difference  & $100$                & $-0.007$                               & $0.023$                           & $-0.003$ \\
        \hline
        LSTM                & $10$                 & $0.195 (\pm1.1\times 10^{-3})$         & $0.193(\pm1.7\times 10^{-3})$     & $0.070 (\pm9.1\times 10^{-4})$ \\
        High-capacity LSTM  & $10$                 & $0.157 (\pm2.0\times 10^{-3})$         & $0.199(\pm1.9\times 10^{-3})$     & $0.065 (\pm1.9\times 10^{-3})$ \\
        Average Difference  & $10$                 & $-0.038$                               & $0.006$                           & $-0.005$ \\
        \hline
        LSTM                & $1$                  & $1.366 (\pm8.6\times 10^{-3})$         & $0.781(\pm6.0\times 10^{-3})$     & $0.129 (\pm5.0\times 10^{-3})$ \\
        High-capacity LSTM  & $1$                  & $1.354 (\pm2.7\times 10^{-2})$         & $0.795(\pm8.3\times10^{-2})$      & $0.149 (\pm2.7\times 10^{-2})$ \\
        Average Difference  & $1$                  & $-0.012$                               & $0.014$                           & \textcolor{red}{$0.020$} \\
        \bottomrule
    \end{tabular}
    \caption{MSEs of LSTM metamodels.}
    \label{tab:lstm_arch}
\end{table}

@@

The accuracy and robustness of the LSTM metamodels motivate us to propose a single-stage procedure that uses the metamodel predictions to estimate the CVaR directly. 
Instead of relying on the standard nested simulation procedure in stage 2, the single-stage procedure can be even more efficient.
In this section, we compare the single-stage procedure to the two-stage procedure and the standard procedure in estimating the $95\%$-CVaR of the hedging losses for GMWB.
In our numerical experiments, the results for the single-stage procedure is obtained with the same metamodels as in the two-stage procedure.
The only difference from Section~\ref{subsec:twoStageProcedure} is that the metamodel predictions are used to estimate the risk measures directly.
